%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Abir Pal} \\ \vspace{1pt}
    \href{mailto:abir.pal899@gmail.com}{\underline{abir.pal899@gmail.com}} $|$ 
    \href{https://linkedin.com/in/imabp}{\underline{linkedin.com/in/imabp}} $|$
    \href{https://github.com/imabp}{\underline{github.com/imabp}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Major League Hacking}{Remote}
      {Engineering Fellow}{January 2021 -- April 2021}
      \resumeItemListStart
        \resumeItem{Selected as one among the 150 M.L.H Fellows, out of 43,000 Applicants. }
         \resumeItem{Used React and TypeScript at a scale to build devtools and data ethics products.}
         \resumeItem{Worked in a team to compete in four global hackathons.}
         \resumeItem{Won two sprints globally at first prize.}
     \resumeItemListEnd

    \resumeSubheading
      {Hack The Mountains}{Remote}
      {Hackathon Manager and Developer Team Lead}{December 2020 -- April 2021}
      \resumeItemListStart
        \resumeItem{Engineered a Hackathon Website from development to production, and lead the team of developers which generated 80 percent increase in traffic and created a promising revenue model.}
        \resumeItem{Created utility software and dashboard software for Hackathon including mentor support, query system, speaker management and workshop alerts. Contributed in streamlining recruiting panel as a core advisor.}
        
    
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://www.cryptodrive.tech/}{CryptoDrive: Decentralized File storing and sharing service}}{[ ReactJS, Node, IPFS, Solidity,]}}{March 2021}
          \resumeItemListStart
            \resumeItem{ Worked on integration of smart contracts written in Solidity with Web3 and React Client.}
            \resumeItem{ Implemented Lossless data compression algorithms to make things optimized on client side.}
            \resumeItem{ Brainstormed and successfully, managed and developed the product.}
            \resumeItem{ Worked in a dedicated team of 3 members, and reviewed Pull Requests and used Team Collaboration tools. }
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
     \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://imabp.github.io/WebTerminal/}{Web Terminal : Linux Simulation on Web Browsers}}{[React, Data Structures]}}{December 2020}
          \resumeItemListStart
            \resumeItem{Empowered beginners to get started with Linux Commands, via Web Terminal, a simulated terminal on browser. }
            \resumeItem{Developed File Service System, using Tree Data Structures. }
          \resumeItemListEnd
    \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/imabp/CertiGen}{\textbf{CertiGen}}}{ [NodeJS, JIMP and Postman]}}{October 2020}
          \resumeItemListStart
            \resumeItem{A devtool for Microsoft Student Ambassadors, to create certificates in seconds. }
            \resumeItem{Actively used by 1000+ Student Ambassadors, for their events and quick certificate generations. }
            \resumeItem{Using Postman Monitor and Newman Integrated to perform health checks.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, TypeScript, Solidity, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, Airtable API, Material-UI, Interplanetary File Service System  } \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Azure Web Apps, AsyncAPI, OpenAPI, Postman} \\
     \textbf{Libraries}{: React-Router, MongooseJS, Newman }
    }}
 \end{itemize}


%-------------------------------------------
\section{Awards and Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small\item{\resumeItemListStart
        \resumeItem{\textbf{Selected as M.L.H Fellow out of 43,000 applications}}
        \resumeItem{\textbf{Global Hackathon Winner at MLH Fellowship for CryptoDrive} Competed with 150 Experienced Fellows in building products in data ethics. }
        \resumeItem{\textbf{Postman Certified Expert}: Postman Certified Experts are proficient in the essential skills involved in building, maintaining, monitoring and testing API requests, collections and workspaces in Postman. }
        \resumeItem{\textbf{Guest Speaker at Carnegie Mellon University, UC Berkeley and Georgia Tech}: Invited to speak on Secure API Designs and API Literacy at the mentioned universities, infront of the panel from Google Brain and Facebook Research.}
      \resumeItemListEnd
    }
 \end{itemize}
 \section{Volunteer Experience}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \resumeItemListStart
        \resumeItem{\textbf{Postman Student Leader} Selected as one of the 11 Student Leaders, representing Global Advocacy for API Literacy at Postman and featured on official Postman.}
        \resumeItem{\textbf{Microsoft Student Ambassador}: Leveraged 5000+ Students through my talks, articles and sessions in tech and building personal brand.}
      \resumeItemListEnd
    }}
 \end{itemize}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chandigarh University}{Mohali, Punjab}
      {Junior,B.E in Computer Science and Engineering}{August 2018 -- Expected July. 2022}
  \resumeSubHeadingListEnd




\end{document}
